\begin{abstract}
Every generation of AI systems introduces a new abstraction. Yesterday, many applications were built around individual language models. Today, modern AI systems combine models, tools, memory, retrieval, planning, verification, and agent workflows. Tomorrow's systems may add latent reasoning, persistent world models, semantic representations beyond prompts, or architectures not yet named. The execution substrate should not need to change every time.

Foundation models have become increasingly capable. Agent frameworks have become increasingly sophisticated. Execution has become increasingly fragmented.
Modern AI systems already contain agent SDKs, graph runtimes, provider gateways, tool protocols, durable workflow engines, caching layers, observability platforms, and evaluation systems. The problem is no longer that execution infrastructure does not exist. The problem is that execution infrastructure does not compose into a reusable object of optimization.

This paper proposes \migaki, an execution optimizer for AI systems. The v0.4 thesis is evidence-first: before an optimizer can safely skip, reroute, compress, or replay work, it must record what actually happened. \migaki{} therefore begins by representing agent trajectories as graph-shaped traces: agent steps, model calls, tool calls, handoffs, outputs, errors, usage, and cache metadata. Repeated runs can then be compared to identify exact reusable nodes. Only after reuse is detected and justified should a runtime replay cached outputs or transform future execution.

\migaki{} separates what an AI system intends to compute from how that computation is realized across models, providers, tools, context, memory, caches, validators, and runtimes. It introduces \mir, a provider-neutral intermediate representation for logical execution plans, and trajectory graphs for observed runs. Applications and frameworks decide strategy. \migaki{} records, compares, optimizes, lowers, replays, and emits evidence so optimization remains measurable rather than opaque. Every successful computing platform eventually separated describing computation from executing computation; this paper argues that AI systems are approaching the same transition.
\end{abstract}
