\section{The Missing Middle}

Agent frameworks decide what should happen next. Gateways route model requests. Workflow engines preserve durable state. Provider APIs expose model-specific capabilities. Tool protocols expose external systems. Observability platforms record behavior. Evaluation systems measure outcomes.

Each layer owns part of execution. Few layers can optimize across the whole execution graph, and even fewer preserve execution as a reusable artifact. A single agentic workflow may require decisions across all of the following:

\begin{itemize}[leftmargin=1.5em]
  \item model selection and provider routing;
  \item retry, fallback, and timeout policy;
  \item retrieval ordering and context assembly;
  \item duplicate context elimination and prompt-cache layout;
  \item tool-call parallelization and side-effect control;
  \item validation, regression testing, and human approval;
  \item cost accounting, latency budgeting, and audit replay;
  \item provider allowlists, data-retention rules, and trace redaction.
\end{itemize}

These decisions interact. A cache decision may depend on context layout. A routing decision may depend on privacy class. A retry policy may depend on idempotency. A validation policy may change whether lossy compression is acceptable. Local optimization is therefore insufficient.

The missing middle is not merely another runtime component. It is a representation boundary. The system needs a portable record that can answer:

\begin{itemize}[leftmargin=1.5em]
  \item which model and tool operations were executed;
  \item which inputs, dependencies, runtime assumptions, and schemas shaped them;
  \item which outputs, errors, usage, and validation results were produced;
  \item which nodes could be reused in a later run without changing declared behavior;
  \item which nodes could not be reused, and why.
\end{itemize}

\begin{claim}[Execution graph as optimization boundary]
The unit of optimization in agentic systems should not be a single prompt or model call. It should be the full model/tool/retrieval/context trajectory, recorded as a graph with evidence.
\end{claim}
