\section{Cache Planning}

Provider APIs increasingly expose prompt caching behavior. OpenAI documents automatic prompt caching that can reduce latency and input token costs for repeated prompt prefixes \citep{openai_prompt_caching}. Anthropic documents prompt caching with automatic caching, explicit cache breakpoints, TTL behavior, and cache-control semantics \citep{anthropic_prompt_caching,anthropic_costs}.

For a model-call node $v$, let its input be divided into cached-read tokens $h_v$, cache-write tokens $w_v$, fresh input tokens $f_v$, and output tokens $o_v$. A simple provider-specific cost estimate is
\begin{equation}
\Cost_v = c^{\mathrm{read}}_{p(v)} h_v + c^{\mathrm{write}}_{p(v)} w_v + c^{\mathrm{input}}_{p(v)} f_v + c^{\mathrm{output}}_{p(v)} o_v,
\label{eq:cache_cost}
\end{equation}
where $p(v)$ is the provider/backend chosen for node $v$. A cache-planning pass minimizes expected cost and latency by arranging stable context in prefixes, preserving repeated system/developer instructions, and placing provider-specific cache boundaries when supported:
\begin{equation}
\min_c \sum_{v \in V_{\mathrm{model}}} \mathbb{E}[\Cost_v(c)]
\quad \text{subject to} \quad c \in \mathcal{C}_{p(v)}.
\end{equation}
Here $\mathcal{C}_{p(v)}$ represents the cache capabilities of the selected provider, such as automatic prefix caching or explicit breakpoints.

For agent trajectories, cache planning should be staged. First, record cache keys and provider assumptions. Second, compare two graphs and identify exact cache-key matches. Third, estimate avoidable model calls, tool calls, tokens, latency, and cost. Fourth, replay only when validators and policy allow it.

\begin{principle}[Cache metadata before cache replay]
The first useful cache system for agentic workflows is not one that skips work. It is one that records enough evidence to know which work could have been skipped.
\end{principle}

This avoids the easiest failure mode: serving stale garbage with confidence. A \texttt{MigakiCacheKey} can make reuse inspectable before any runtime is allowed to reuse it.
