\begin{thebibliography}{99}

\bibitem{openai_agents_python}
OpenAI.
\newblock \emph{OpenAI Agents SDK: Agents}.
\newblock \url{https://openai.github.io/openai-agents-python/agents/}. Accessed 2026-06-28.

\bibitem{openai_agents_js}
OpenAI.
\newblock \emph{OpenAI Agents SDK for JavaScript/TypeScript}.
\newblock \url{https://github.com/openai/openai-agents-js}. Accessed 2026-06-28.

\bibitem{migaki_openai_agents_js}
Migaki Project.
\newblock \emph{migaki-openai-agents-js instrumentation package}.
\newblock \url{https://github.com/migaki-dev/migaki/tree/main/packages/migaki-openai-agents-js}. Accessed 2026-07-01.

\bibitem{openai_agents_tracing}
OpenAI.
\newblock \emph{Tracing - OpenAI Agents SDK}.
\newblock \url{https://openai.github.io/openai-agents-python/tracing/}. Accessed 2026-06-28.

\bibitem{openai_agents_running}
OpenAI.
\newblock \emph{Running agents - OpenAI Agents SDK}.
\newblock \url{https://openai.github.io/openai-agents-python/running_agents/}. Accessed 2026-06-28.

\bibitem{openai_prompt_caching}
OpenAI.
\newblock \emph{Prompt caching - OpenAI API}.
\newblock \url{https://developers.openai.com/api/docs/guides/prompt-caching}. Accessed 2026-06-28.

\bibitem{anthropic_prompt_caching}
Anthropic.
\newblock \emph{Prompt caching - Claude Platform Docs}.
\newblock \url{https://docs.anthropic.com/en/docs/build-with-claude/prompt-caching}. Accessed 2026-06-28.

\bibitem{anthropic_costs}
Anthropic.
\newblock \emph{Manage costs effectively - Claude Code Docs}.
\newblock \url{https://docs.anthropic.com/en/docs/claude-code/costs}. Accessed 2026-06-28.

\bibitem{langgraph_overview}
LangChain.
\newblock \emph{LangGraph overview}.
\newblock \url{https://docs.langchain.com/oss/python/langgraph/overview}. Accessed 2026-06-28.

\bibitem{google_adk}
Google Cloud.
\newblock \emph{Agent Development Kit documentation}.
\newblock \url{https://docs.cloud.google.com/gemini-enterprise-agent-platform/build/adk}. Accessed 2026-06-28.

\bibitem{microsoft_agent_framework}
Microsoft.
\newblock \emph{Microsoft Agent Framework documentation}.
\newblock \url{https://learn.microsoft.com/en-us/agent-framework/}. Accessed 2026-06-28.

\bibitem{litellm_routing}
LiteLLM.
\newblock \emph{Routing strategies - LiteLLM docs}.
\newblock \url{https://docs.litellm.ai/docs/routing}. Accessed 2026-06-28.

\bibitem{cloudflare_ai_gateway}
Cloudflare.
\newblock \emph{Cloudflare AI Gateway}.
\newblock \url{https://developers.cloudflare.com/ai-gateway/}. Accessed 2026-06-28.

\bibitem{vercel_ai_gateway_observability}
Vercel.
\newblock \emph{AI Gateway observability}.
\newblock \url{https://vercel.com/docs/ai-gateway/observability-and-spend/observability}. Accessed 2026-06-28.

\bibitem{vercel_fallbacks}
Vercel.
\newblock \emph{Model fallbacks now available in Vercel AI Gateway}.
\newblock \url{https://vercel.com/changelog/model-fallbacks-now-available-in-vercel-ai-gateway}. Accessed 2026-06-28.

\bibitem{temporal_agents}
Temporal.
\newblock \emph{Of course you can build dynamic AI agents with Temporal}.
\newblock \url{https://temporal.io/blog/of-course-you-can-build-dynamic-ai-agents-with-temporal}. Accessed 2026-06-28.

\bibitem{mcp_tools}
Model Context Protocol.
\newblock \emph{Tools - Model Context Protocol Specification}.
\newblock \url{https://modelcontextprotocol.io/specification/2025-03-26/server/tools}. Accessed 2026-06-28.

\bibitem{otel_genai}
OpenTelemetry.
\newblock \emph{Semantic Conventions for Generative AI}.
\newblock \url{https://github.com/open-telemetry/semantic-conventions-genai}. Accessed 2026-06-28.

\bibitem{langfuse_docs}
Langfuse.
\newblock \emph{Langfuse documentation}.
\newblock \url{https://langfuse.com/docs}. Accessed 2026-06-28.

\bibitem{routellm}
Ong, I., Almahairi, A., Wu, V., Chiang, W.-L., Wu, T., Gonzalez, J. E., Kadous, M. W., and Stoica, I.
\newblock RouteLLM: Learning to Route LLMs with Preference Data.
\newblock \emph{arXiv preprint arXiv:2406.18665}, 2024. \url{https://arxiv.org/abs/2406.18665}.

\bibitem{llmrouterbench}
Li, H., Zhang, Y., Guo, Z., Wang, C., Tang, S., Zhang, Q., Yang, C., Qi, B., Ye, P., Bai, L., Wang, Z., and Hu, S.
\newblock LLMRouterBench: A Massive Benchmark and Unified Framework for LLM Routing.
\newblock \emph{arXiv preprint arXiv:2601.07206}, 2026. \url{https://arxiv.org/abs/2601.07206}.

\end{thebibliography}
